---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  pdf_document: default
---


```{r}
# install.packages("tidyverse")
# install.packages("readxl")
# install.packages("psych")
# install.packages("gridExtra")

library(psych)
library(scales)
library(gridExtra)
library(tidyverse)
library(readxl)
library(knitr)
```

Read data
``` {r}
CallCentreUrl <- "data/callcentre_06.xlsx"
HRMUrl <- "data/HRM_06.xlsx"
CallCentreData <- read_excel(CallCentreUrl)
HRMData <- read_excel(HRMUrl)
```

CallCentre data description
``` {r}
str(CallCentreData)
```

CallCentre data summary
``` {r}
summary(CallCentreData)
```

HRM data description
``` {r}
str(HRMData)
```

HRM data summary
``` {r}
summary(HRMData)
```

Number of call by time

``` {r}
CallCentreData %>% count(time)
```
``` {r}
 options(scipen = 3)
CallCentreData %>% 
    count(time) %>%
    mutate(percentage = n / sum(n) * 100)
```

```{r}
CallCentreData %>% count(time) %>% 
  ggplot(. , aes(x = time, y = n ))  + 
  geom_bar( stat="identity", position=position_dodge(),
            fill="#4126de", color="#e9ecef", alpha=0.9) +
            ylab("Number of call") + 
            xlab("Time of the day (in hours)") +
            geom_text(aes(label=n),
                             vjust= - 0.5,
                             position = position_dodge(0.9),
                             size=2.5) +
            ggtitle("Number Of Call By Time") +
            theme_minimal()
```

Average duration of the call by time
``` {r}
CallCentreData %>% group_by(time) %>% summarise(mean = mean(length, na.rm = TRUE))
```
``` {r}
CallCentreData %>% group_by(time) %>% summarise(mean = round(mean(length, na.rm = TRUE))) %>% 
  ggplot(. , aes(x = time, y = mean ))  + 
  geom_bar( stat="identity", position=position_dodge(),
            fill="#69b3a2", color="#e9ecef", alpha=0.9) +
            ylab("Average length of time") + 
            xlab("Time of the day (in hours)") +
            geom_text(aes(label= mean),
                             vjust= - 0.5,
                             position = position_dodge(0.9),
                             size=2.5) +
            geom_hline(yintercept = mean(CallCentreData$length), color="#fc0303") +
            geom_text(aes(y= mean(CallCentreData$length), x= 1),
                      label= paste("Average of all time:", round(mean(CallCentreData$length))),
                      hjust= 0, vjust= -1, size= 3.5)+ 
            ggtitle("Average Length Of Time Of The Call By Time") +
            theme_minimal() 
```
% of problem
``` {r}
CallCentreData %>% 
                  count(problem)  %>%
                  mutate(percentage= n/sum(n)*100) %>%
                  arrange(desc(n))
```

``` {r}
CallCentreData %>% 
                  count(problem)  %>%
                  mutate(percentage= n/sum(n)*100) %>%
                  mutate(percentage= round(percentage, 1)) %>%
                  mutate(labels=  paste(problem, " (", percentage, "%)", sep = "" )) -> problemPie

library(RColorBrewer)
myPalette <- brewer.pal(5, "Set2") 
pie(problemPie$n , labels = problemPie$labels, border="white", col=myPalette,
    main = "Percentage Of Problem")

```
% of forward
``` {r}
CallCentreData %>% 
                  mutate(forwarded = recode(forwarded, "forwarded" = "forwarded", "NA" = "not forwarded")) %>%
                  count(forwarded)  %>%
                  mutate(percentage= n/sum(n)*100)
```
``` {r}
CallCentreData %>% 
                  mutate(forwarded = recode(forwarded, "forwarded" = "forwarded", "NA" = "not forwarded")) %>%
                  count(forwarded)  %>%
                  mutate(percentage= n/sum(n)*100) %>%
                  mutate(yposition = cumsum(percentage)- 0.5*percentage ) %>%
                  mutate(percentage= round(percentage, 1)) %>%
  
ggplot(., aes(x="", y= percentage, fill= forwarded)) +
        geom_bar(stat="identity", width=1, color="white") +
        coord_polar("y", start=0) +
        theme_void(base_size = 13) + theme(legend.position = "none") +
        ggtitle("Percentage Forwarded") +
        geom_text(aes(y = yposition, label = paste(forwarded, "\n", n, " (", percentage, "%)", sep = "")),
                  color = "white", size= 4) +
        scale_fill_brewer(palette="Set1")
```
forward by time
``` {r}
CallCentreData %>% 
  mutate(forwarded = recode(forwarded, "forwarded" = "forwarded", "NA" = "not forwarded")) %>%                
  count(time, forwarded) %>% spread(forwarded, n) %>%
  replace_na(list("forwarded" = 0, "not forwarded" = 0))
```
``` {r}
CallCentreData %>% 
  mutate(forwarded = recode(forwarded, "forwarded" = "forwarded", "NA" = "not forwarded")) %>%                
  count(time, forwarded) %>%
ggplot(., aes(x= time, y= n, fill= forwarded)) +
        geom_bar(stat="identity") + 
        theme(legend.title=element_blank()) +
        ggtitle("Forwarded By Time")+
        ylab("Average length of time") + 
        xlab("Time of the day (in hours)")

```
Overoll satisfaction
``` {r}
summary(CallCentreData$customer_satisfaction)
```
``` {r}
boxplot(CallCentreData$customer_satisfaction,
main = "Satisfaction With The Service",
xlab = "Customer satisfaction score",
col = "orange",
border = "brown",
horizontal = TRUE,
notch = TRUE
)
```


``` {r}
CallCentreData %>% filter(!is.na(customer_satisfaction)) %>%
  mutate(satisfaction_group = ifelse(customer_satisfaction < 5, "Low",
                                     ifelse(customer_satisfaction < 8, "Middle", "Hight")) ) %>%
  count(satisfaction_group) %>% 
  mutate(percentage= n/sum(n)*100)
  
```
```{r}
 
CallCentreData %>% filter(!is.na(customer_satisfaction)) %>%
  mutate(satisfaction_group = ifelse(customer_satisfaction < 5, "Low",
                                     ifelse(customer_satisfaction < 8, "Middle", "Hight")) ) %>%
  count(satisfaction_group) %>% 
  mutate(percentage= n/sum(n)*100)



```



```{r}
CallCentreData %>% 
                  group_by(customer_satisfaction)  %>%
                  count()
```
``` {r}
CallCentreData %>% count(customer_satisfaction) %>% 
  ggplot(. , aes(x = customer_satisfaction, y = n ))  + 
  geom_bar( stat="identity", position=position_dodge(), alpha=0.9) +
            ylab("Number of call") + 
            xlab("Customer satisfaction score") +
            geom_text(aes(label=n),
                             vjust= - 0.5,
                             position = position_dodge(0.9),
                             size=2.5) +
            ggtitle("Satisfaction With The Service") +
            theme_minimal()
```

satisfaction by duration
```{r}
CallCentreData %>% 
                  group_by(customer_satisfaction)  %>%
                  summarise(mean_length = mean(length),
                            mean_waiting = mean(waiting))
```

```{r}
ggplot(CallCentreData, aes(y= length, x = customer_satisfaction)) + 
    geom_point(aes(color = "blue"), alpha = 0.8) + 
    geom_smooth(formula = y~x, method="lm") + 
    ggtitle("Satisfaction By Duration Of The Call") +
    xlab("Customer satisfaction score") + 
    ylab("Duration of the call") +
    theme_bw(base_size =  12) + theme(legend.position = "none") 
```


``` {r}
ggplot( CallCentreData, aes(y= as_factor(customer_satisfaction), fill= as_factor(customer_satisfaction), x= length)) +
  geom_boxplot()  +
  ggtitle("Satisfaction By Duration Of The Call") +
  xlab("Duration of the call") + 
  ylab("Customer satisfaction score") +
  theme(legend.position = "none") 
```

satisfaction by waiting

```{r}
ggplot(CallCentreData, aes(y= waiting, x = customer_satisfaction)) + 
    geom_point(aes(color = "blue"), alpha = 0.8) + 
    geom_smooth(formula = y~x, method="lm") + 
    ggtitle("Satisfaction By Waiting Time") +
    xlab("Customer satisfaction score") + 
    ylab("Waiting time") +
    theme_bw(base_size =  12) + theme(legend.position = "none") 
```
``` {r}
ggplot( CallCentreData, aes(y= as_factor(customer_satisfaction), fill= as_factor(customer_satisfaction), x= waiting)) +
  geom_boxplot()  +
  ggtitle("Satisfaction By Waiting Time") +
  xlab("Waiting time") + 
  ylab("Customer satisfaction score") +
  theme(legend.position = "none") 
```
satisfaction by problem
``` {r}
CallCentreData %>% 
                  group_by(problem)  %>%
                  summarise(
                            Min = min(customer_satisfaction, na.rm = TRUE),
                            "1st Quantile" = quantile(customer_satisfaction, probs = c(0.25), na.rm = TRUE),
                            Median = median(customer_satisfaction, na.rm = TRUE),
                            Mean = mean(customer_satisfaction, na.rm = TRUE),
                            "3st Quantile" = quantile(customer_satisfaction, probs = c(0.75), na.rm = TRUE),
                            Max = max(customer_satisfaction, na.rm = TRUE),
                            Missing = sum(is.na(customer_satisfaction))
)
```

``` {r}
ggplot( CallCentreData, aes(y= problem, fill=problem, x= customer_satisfaction)) +
  geom_boxplot()  +
  ggtitle("Satisfaction By Problem") +
  ylab("") + 
  xlab("Customer satisfaction score") + 
  theme(
        axis.text.y = element_blank(),
        axis.ticks = element_blank())
```
waiting time
```{r}
summary(CallCentreData$waiting)
```

``` {r}
boxplot(CallCentreData$waiting,
main = "Waiting time",
xlab = "Waiting time in second",
col = "orange",
border = "brown",
horizontal = TRUE,
notch = TRUE
)
```

``` {r}
CallCentreData %>% filter(!is.na(waiting)) %>%
  mutate(waiting_group = ifelse(waiting < 60, "< 60s",
                                     ifelse(waiting <= 120, "60s - 120s", "> 120s")) ) %>%
  count(waiting_group) %>% 
  mutate(percentage= n/sum(n)*100)
  
```

agent performance by munber of call

``` {r}
CallCentreData %>% 
                  count(agent)  %>%
                  arrange(desc(n))
```
``` {r}
CallCentreData %>% 
                  count(agent)  %>%
                  mutate(agent = paste("Agent", agent)) %>%
                  arrange(desc(n)) %>% head(10) %>% 
                  mutate(agent = fct_reorder(agent, n)) %>%
  ggplot(., aes(x = n, y = agent)) +
  geom_segment( aes(x= 0, xend= n, y= agent, yend= agent), color="blue") +
  geom_point( color="green", size=4) +
  theme_light() +
  theme(
    panel.grid.major.x = element_blank(),
    panel.border = element_blank(),
    axis.ticks.x = element_blank()
  ) +
  xlab("") + xlim(0, 2500) +
  ylab("") + ggtitle("Top 10") -> Top10byCall

CallCentreData %>% 
                  count(agent)  %>%
                  mutate(agent = paste("Agent", agent)) %>%
                  arrange(desc(n)) %>% tail(10) %>% 
                  mutate(agent = fct_reorder(agent, n)) %>%
  ggplot(., aes(x = n, y = agent)) +
  geom_segment( aes(x= 0, xend= n, y= agent, yend= agent), color="red") +
  geom_point( color="red", size=4) +
  theme_light() +
  theme(
    panel.grid.major.x = element_blank(),
    panel.border = element_blank(),
    axis.ticks.x = element_blank()
  ) +
  xlab("") + xlim(0, 2500) +
  ylab("") + ggtitle("Bottom 10")  -> Tail10byCall

grid.arrange(Top10byCall, Tail10byCall, nrow= 1, ncol = 2, 
             top = "Agent Ranking By Number Of Call")
```
agent performance by sum duration of the call
``` {r}
CallCentreData %>% 
                  group_by(agent)  %>%
                  summarise("Sum_length" = sum(length, na.rm = TRUE)) %>%
                  arrange(desc(Sum_length))
```
``` {r}
CallCentreData %>% 
                  group_by(agent)  %>%
                  summarise(n = sum(length, na.rm = TRUE)) %>%
                  mutate(agent = paste("Agent", agent)) %>%
                  arrange(desc(n)) %>% mutate(agent = fct_reorder(agent, n)) %>%
                  head(10) %>%
  ggplot(., aes(x = n, y = agent)) +
  geom_segment( aes(x= 0, xend= n, y= agent, yend= agent), color="blue") +
  geom_point( color="green", size=4) +
  theme_light() +
  theme(
    panel.border = element_blank(),
  ) +
  xlab("") + ggtitle("Top 10") + scale_x_continuous(labels = number, limits= c(0, 800000) ) +
  ylab("") -> Top10byDuration

CallCentreData %>% 
                  group_by(agent)  %>%
                  summarise(n = sum(length, na.rm = TRUE)) %>%
                  mutate(agent = paste("Agent", agent)) %>%
                  arrange(desc(n)) %>% mutate(agent = fct_reorder(agent, n)) %>%
                  tail(10) %>%
  ggplot(., aes(x = n, y = agent)) +
  geom_segment( aes(x= 0, xend= n, y= agent, yend= agent), color="red") +
  geom_point( color="red", size=4) +
  theme_light() +
  theme(
    panel.border = element_blank(),
  ) +
  xlab("") + ggtitle("Bottom 10") + scale_x_continuous(labels = number, limits= c(0, 800000) ) +
  ylab("")  -> Tail10byDuration

grid.arrange(Top10byDuration, Tail10byDuration, nrow= 1, ncol = 2, 
             top = "Agent Ranking By Sum Duration Of The Call")
```


agent performance by satisfaction

``` {r}
CallCentreData %>% 
                  group_by(agent)  %>%
                  summarise("Mean_satisfaction" = mean(customer_satisfaction, na.rm = TRUE)) %>%
                  arrange(desc(Mean_satisfaction))
```
``` {r}
CallCentreData %>% 
                  group_by(agent)  %>%
                  summarise(n = mean(customer_satisfaction, na.rm = TRUE)) %>%
                  mutate(agent = paste("Agent", agent)) %>%
                  arrange(desc(n)) %>% mutate(agent = fct_reorder(agent, n)) %>%
                  head(10) %>%
  ggplot(., aes(x = n, y = agent)) +
  geom_segment( aes(x= 0, xend= n, y= agent, yend= agent), color="blue") +
  geom_point( color="green", size=4) +
  theme_light() +
  theme(
    panel.border = element_blank(),
  ) +
  xlab("") + ggtitle("Top 10") + scale_x_continuous(labels = number, limits= c(0, 10) ) +
  ylab("") -> Top10bySatisfaction

CallCentreData %>% 
                  group_by(agent)  %>%
                  summarise(n = mean(customer_satisfaction, na.rm = TRUE)) %>%
                  mutate(agent = paste("Agent", agent)) %>%
                  arrange(desc(n)) %>% mutate(agent = fct_reorder(agent, n)) %>%
                  tail(10) %>%
  ggplot(., aes(x = n, y = agent)) +
  geom_segment( aes(x= 0, xend= n, y= agent, yend= agent), color="red") +
  geom_point( color="red", size=4) +
  theme_light() +
  theme(
    panel.border = element_blank(),
  ) +
  xlab("") + ggtitle("Bottom 10") + scale_x_continuous(labels = number, limits= c(0, 10) ) +
  ylab("")  -> Tail10bySatisfaction

grid.arrange(Top10bySatisfaction, Tail10bySatisfaction, nrow= 1, ncol = 2, 
             top = "Agent Ranking By Customer Satisfaction")
```

agent performance by waiting time
``` {r}
CallCentreData %>% 
                  group_by(agent)  %>%
                  summarise("Mean_waiting" = mean(waiting, na.rm = TRUE)) %>%
                  arrange(desc(Mean_waiting))
```
``` {r}
CallCentreData %>% 
                  group_by(agent)  %>%
                  summarise(n = mean(waiting, na.rm = TRUE)) %>%
                  mutate(agent = paste("Agent", agent)) %>%
                  arrange(desc(n)) %>% mutate(agent = fct_reorder(agent, desc(n))) %>%
                  head(10) %>%
  ggplot(., aes(x = n, y = agent)) +
  geom_segment( aes(x= 0, xend= n, y= agent, yend= agent), color="red") +
  geom_point( color="red", size=4) +
  theme_light() +
  theme(
    panel.border = element_blank(),
  ) +
  xlab("") + ggtitle("Top 10") + scale_x_continuous(labels = number, limits= c(0, 60) ) +
  ylab("") -> Tail10byWaiting

CallCentreData %>% 
                  group_by(agent)  %>%
                  summarise(n = mean(waiting, na.rm = TRUE)) %>%
                  mutate(agent = paste("Agent", agent)) %>%
                  arrange(desc(n)) %>% mutate(agent = fct_reorder(agent, desc(n))) %>%
                  tail(10) %>%
  ggplot(., aes(x = n, y = agent)) +
  geom_segment( aes(x= 0, xend= n, y= agent, yend= agent), color="blue") +
  geom_point( color="green", size=4) +
  theme_light() +
  theme(
    panel.border = element_blank(),
  ) +
  xlab("") + ggtitle("Bottom 10") + scale_x_continuous(labels = number, limits= c(0, 60) ) +
  ylab("")  -> Top10byWaiting

grid.arrange(Top10byWaiting, Tail10byWaiting, nrow= 1, ncol = 2, 
             top = "Agent Ranking By Waiting Time")
```

agent by problem
``` {r}
CallCentreData %>% 
                  group_by(agent, problem)  %>%
                  count(problem)%>%
                  spread(problem, n)
```
allocation of agent by gender
``` {r}
HRMData %>% 
           count(gender)  %>%
           mutate(percentage= n/sum(n)*100)
```


``` {r}
HRMData %>% 
           filter(!is.na(gender)) %>%         
           count(gender)  %>%
           arrange(desc(n)) %>%
           mutate(percentage= n/sum(n)*100) %>%
           mutate(yposition = cumsum(percentage)- 0.5*percentage ) %>%
           mutate(percentage= round(percentage, 1)) %>%
  
ggplot(., aes(x="", y= percentage, fill= gender)) +
        geom_bar(stat="identity", width=1, color="white") +
        coord_polar("y", start=0) +
        theme_void(base_size = 13) + theme(legend.position = "none") +
        ggtitle("Percentage Gender") +
        geom_text(aes(y = yposition, label = paste(gender, "\n", n, " (", percentage, "%)", sep = "")),
                  color = "white", size= 4) 
```
agent by tenure
``` {r}
summary(HRMData$tenure)
```

``` {r}
# color=group, fill=group
ggplot(HRMData, aes(x=tenure)) +
    geom_histogram(aes(y=..density..), fill="#999999", bins=20, position="identity", alpha=0.7)+
    geom_density(alpha=0.6, color="darkblue", fill="lightblue")+
    labs(title="Distribution Of Agent Tenure",x="Number of months", y = "Density")+  
    theme_classic(base_size = 14) +
    geom_vline(xintercept = mean(HRMData$tenure), color="#fc0303") +
    geom_text(aes(y= 0, x= mean(tenure)),
                      label= paste("Mean:", round(mean(HRMData$tenure))),
                      hjust= -0.1 , vjust= 0, size= 3.5)

```


agent by qualification

``` {r}
HRMData %>%
  count(qualification) %>%
  arrange(desc(n))
```
``` {r}
HRMData %>% 
           filter(qualification != "NA") %>%         
           count(qualification)  %>%
           arrange(desc(n)) %>%
           mutate(percentage= n/sum(n)*100) %>%
           mutate(yposition = cumsum(percentage)- 0.5*percentage ) %>%
           mutate(percentage= round(percentage, 1)) %>%
  
ggplot(., aes(x="", y= percentage, fill= qualification)) +
        geom_bar(stat="identity", width=1, color="white") +
        coord_polar("y", start=0) +
        theme_void(base_size = 10) + theme(legend.position = "none") +
        ggtitle("Percentage Of Education Degree") +
        geom_text(aes(y = yposition, label = paste(qualification, "\n", n, " (", percentage, "%)", sep = "")),
                  color = "white", size= 4) 
```

agent by ethnicity 
``` {r}
HRMData %>%
  count(ethnicity) %>%
  arrange(desc(n))
```

``` {r}
HRMData %>% 
           filter(!is.na(ethnicity)) %>%         
           count(ethnicity)  %>%
           arrange(desc(n)) %>%
           mutate(percentage= n/sum(n)*100) %>%
           mutate(yposition = cumsum(percentage)- 0.5*percentage ) %>%
           mutate(percentage= round(percentage, 1)) %>%
  
ggplot(., aes(x="", y= percentage, fill= ethnicity)) +
        geom_bar(stat="identity", width=1, color="white") +
        coord_polar("y", start=0) +
        theme_void(base_size = 10) + theme(legend.position = "none") +
        ggtitle("Percentage Of Employee’s Ethnic") +
        geom_text(aes(y = yposition, label = paste(ethnicity, "\n", n, " (", percentage, "%)", sep = "")),
                  color = "white", size= 4) 
```

Combine Data
``` {r}
CallCentreData$agent <- as.numeric(CallCentreData$agent)
HRMData$agent <- as.numeric(HRMData$agent)
CombineData <- left_join(CallCentreData, HRMData, by = "agent")
```

satisfaction by gender
``` {r}
CombineData %>% 
                  group_by(gender)  %>%
                  summarise(
                            Count = n(),        
                            Min = min(customer_satisfaction, na.rm = TRUE),
                            "1st Quantile" = quantile(customer_satisfaction, probs = c(0.25), na.rm = TRUE),
                            Median = median(customer_satisfaction, na.rm = TRUE),
                            Mean = mean(customer_satisfaction, na.rm = TRUE),
                            "3st Quantile" = quantile(customer_satisfaction, probs = c(0.75), na.rm = TRUE),
                            Max = max(customer_satisfaction, na.rm = TRUE),
                            Missing = sum(is.na(customer_satisfaction))
)
```
``` {r}
CombineData %>% filter(!is.na(gender)) %>% filter(gender != "NA") %>%
  ggplot( ., aes(y= gender, fill=gender, x= customer_satisfaction)) +
  geom_boxplot()  +
  ggtitle("Satisfaction By Sex") +
  ylab("Sex") + 
  xlab("Satisfaction") + 
  theme(
        axis.text.y = element_blank(),
        axis.ticks = element_blank())
```
```{r}
t.test(data = CombineData, customer_satisfaction ~ gender)
```

Duration by gender
``` {r}
CombineData %>% 
                  group_by(gender)  %>%
                  summarise(
                            Count = n(),        
                            Min = min(length, na.rm = TRUE),
                            "1st Quantile" = quantile(length, probs = c(0.25), na.rm = TRUE),
                            Median = median(length, na.rm = TRUE),
                            Mean = mean(length, na.rm = TRUE),
                            "3st Quantile" = quantile(length, probs = c(0.75), na.rm = TRUE),
                            Max = max(length, na.rm = TRUE),
                            Missing = sum(is.na(length))
)
```
``` {r}
CombineData %>% filter(!is.na(gender)) %>% filter(gender != "NA") %>%
  ggplot( ., aes(y= gender, fill=gender, x= length)) +
  geom_boxplot()  +
  ggtitle("Duration By Sex") +
  ylab("Sex") + 
  xlab("Duration") + 
  theme(
        axis.text.y = element_blank(),
        axis.ticks = element_blank())
```
```{r}
t.test(data = CombineData, length ~ gender)
```

Waiting time by gender
``` {r}
CombineData %>% 
                  group_by(gender)  %>%
                  summarise(
                            Count = n(),        
                            Min = min(waiting, na.rm = TRUE),
                            "1st Quantile" = quantile(waiting, probs = c(0.25), na.rm = TRUE),
                            Median = median(waiting, na.rm = TRUE),
                            Mean = mean(waiting, na.rm = TRUE),
                            "3st Quantile" = quantile(waiting, probs = c(0.75), na.rm = TRUE),
                            Max = max(waiting, na.rm = TRUE),
                            Missing = sum(is.na(waiting))
)
```
``` {r}
CombineData %>% filter(!is.na(gender)) %>% filter(gender != "NA") %>%
  ggplot( ., aes(y= gender, fill=gender, x= customer_satisfaction)) +
  geom_boxplot()  +
  ggtitle("Waiting Time By Sex") +
  ylab("Sex") + 
  xlab("Waiting time") + 
  theme(
        axis.text.y = element_blank(),
        axis.ticks = element_blank())
```
```{r}
t.test(data = CombineData, waiting ~ gender)
```

satisfaction by qualification
``` {r}
CombineData %>% 
                  group_by(qualification)  %>%
                  summarise(
                            Count = n(),        
                            Min = min(customer_satisfaction, na.rm = TRUE),
                            "1st Quantile" = quantile(customer_satisfaction, probs = c(0.25), na.rm = TRUE),
                            Median = median(customer_satisfaction, na.rm = TRUE),
                            Mean = mean(customer_satisfaction, na.rm = TRUE),
                            "3st Quantile" = quantile(customer_satisfaction, probs = c(0.75), na.rm = TRUE),
                            Max = max(customer_satisfaction, na.rm = TRUE),
                            Missing = sum(is.na(customer_satisfaction))
)
```
``` {r}
CombineData %>% filter(!is.na(qualification)) %>% filter(qualification != "NA") %>%
  ggplot( ., aes(y= qualification, fill=qualification, x= customer_satisfaction)) +
  geom_boxplot()  +
  ggtitle("Satisfaction By Qualification") +
  ylab("Qualification") + 
  xlab("Satisfaction") + 
  theme(
        axis.text.y = element_blank(),
        axis.ticks = element_blank())
```
```{r}
CombineData %>% filter(qualification != "NA") %>%
aov(data = ., customer_satisfaction ~ qualification) %>% summary()
```

Duration by qualification
``` {r}
CombineData %>% 
                  group_by(qualification)  %>%
                  summarise(
                            Count = n(),        
                            Min = min(length, na.rm = TRUE),
                            "1st Quantile" = quantile(length, probs = c(0.25), na.rm = TRUE),
                            Median = median(length, na.rm = TRUE),
                            Mean = mean(length, na.rm = TRUE),
                            "3st Quantile" = quantile(length, probs = c(0.75), na.rm = TRUE),
                            Max = max(length, na.rm = TRUE),
                            Missing = sum(is.na(length))
)
```
``` {r}
CombineData %>% filter(!is.na(qualification)) %>% filter(qualification != "NA") %>%
  ggplot( ., aes(y= qualification, fill=qualification, x= length)) +
  geom_boxplot()  +
  ggtitle("Duration By Qualification") +
  ylab("Qualification") + 
  xlab("Duration") + 
  theme(
        axis.text.y = element_blank(),
        axis.ticks = element_blank())
```
```{r}
CombineData %>% filter(qualification != "NA") %>%
aov(data = ., length ~ qualification) %>% summary()
```

Waiting time by qualification
``` {r}
CombineData %>% 
                  group_by(qualification)  %>%
                  summarise(
                            Count = n(),        
                            Min = min(waiting, na.rm = TRUE),
                            "1st Quantile" = quantile(waiting, probs = c(0.25), na.rm = TRUE),
                            Median = median(waiting, na.rm = TRUE),
                            Mean = mean(waiting, na.rm = TRUE),
                            "3st Quantile" = quantile(waiting, probs = c(0.75), na.rm = TRUE),
                            Max = max(waiting, na.rm = TRUE),
                            Missing = sum(is.na(waiting))
)
```
``` {r}
CombineData %>% filter(!is.na(qualification)) %>% filter(qualification != "NA") %>%
  ggplot( ., aes(y= qualification, fill=qualification, x= waiting)) +
  geom_boxplot()  +
  ggtitle("Waiting Time By Qualification") +
  ylab("Qualification") + 
  xlab("Waiting time") + 
  theme(
        axis.text.y = element_blank(),
        axis.ticks = element_blank())
```

``` {r}
CombineData %>% filter(!is.na(qualification)) %>% filter(qualification != "NA") %>%
  ggplot( ., aes(y= qualification, fill=qualification, x= waiting)) +
  geom_boxplot()  +
  ggtitle("Waiting Time By Qualification") +
  ylab("Qualification") + 
  xlab("Waiting time") + 
  theme(
        axis.text.y = element_blank(),
        axis.ticks = element_blank())
```
```{r}
CombineData %>% filter(qualification != "NA") %>%
aov(data = ., waiting ~ qualification) %>% summary()
```
satisfaction by ethnicity
``` {r}
CombineData %>% 
                  group_by(ethnicity)  %>%
                  summarise(
                            Count = n(),
                            Min = min(customer_satisfaction, na.rm = TRUE),
                            "1st Quantile" = quantile(customer_satisfaction, probs = c(0.25), na.rm = TRUE),
                            Median = median(customer_satisfaction, na.rm = TRUE),
                            Mean = mean(customer_satisfaction, na.rm = TRUE),
                            "3st Quantile" = quantile(customer_satisfaction, probs = c(0.75), na.rm = TRUE),
                            Max = max(customer_satisfaction, na.rm = TRUE),
                            Missing = sum(is.na(customer_satisfaction))
)
```
``` {r}
CombineData %>% filter(!is.na(ethnicity)) %>%
ggplot( ., aes(y= ethnicity, fill=ethnicity, x= length)) +
  geom_boxplot()  +
  ggtitle("Satisfaction By Ethnicity") +
  ylab("Ethnicity") + 
  xlab("Satisfaction") + 
  theme(
        axis.text.y = element_blank(),
        axis.ticks = element_blank())
```
```{r}
aov(data = CombineData, customer_satisfaction ~ ethnicity) %>% summary()
```

Duration by ethnicity
``` {r}
CombineData %>% 
                  group_by(ethnicity)  %>%
                  summarise(
                            Count = n(),        
                            Min = min(length, na.rm = TRUE),
                            "1st Quantile" = quantile(length, probs = c(0.25), na.rm = TRUE),
                            Median = median(length, na.rm = TRUE),
                            Mean = mean(length, na.rm = TRUE),
                            "3st Quantile" = quantile(length, probs = c(0.75), na.rm = TRUE),
                            Max = max(length, na.rm = TRUE),
                            Missing = sum(is.na(length))
)
```
``` {r}
CombineData %>% filter(!is.na(ethnicity)) %>%
ggplot( ., aes(y= ethnicity, fill=ethnicity, x= length)) +
  geom_boxplot()  +
  ggtitle("Duration By Ethnicity") +
  ylab("Ethnicity") + 
  xlab("Duration") + 
  theme(
        axis.text.y = element_blank(),
        axis.ticks = element_blank())
```
```{r}
aov(data = CombineData, length ~ ethnicity) %>% summary()
```

Waiting time by ethnicity
``` {r}
CombineData %>% 
                  group_by(ethnicity)  %>%
                  summarise(
                            Count = n(),        
                            Min = min(waiting, na.rm = TRUE),
                            "1st Quantile" = quantile(waiting, probs = c(0.25), na.rm = TRUE),
                            Median = median(waiting, na.rm = TRUE),
                            Mean = mean(waiting, na.rm = TRUE),
                            "3st Quantile" = quantile(waiting, probs = c(0.75), na.rm = TRUE),
                            Max = max(waiting, na.rm = TRUE),
                            Missing = sum(is.na(waiting))
)
```
``` {r}
CombineData %>% filter(!is.na(ethnicity)) %>%
ggplot( ., aes(y= ethnicity, fill=ethnicity, x= waiting)) +
  geom_boxplot()  +
  ggtitle("Waiting Time By Ethnicity") +
  ylab("Ethnicity") + 
  xlab("Waiting time") + 
  theme(
        axis.text.y = element_blank(),
        axis.ticks = element_blank())
```

```{r}
aov(data = CombineData, waiting ~ ethnicity) %>% summary()
```


```{r}
library(psych)
options(repr.plot.width = 12, repr.plot.height = 12)
pairs.panels(CombineData[,c("length", "waiting", "customer_satisfaction", "age", "tenure")], 
             method = "pearson", # correlation method
             hist.col = "#00AFBB",
             density = TRUE,  # show density plots
             ellipses = TRUE # show correlation ellipses
             )
```





















